 

### 2020-07-10 doc/manuscript/tables_figures/sites_table.Rmd
update sites table

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE,  escape = F)%>%
  column_spec(1, width = "2cm") %>%
  column_spec(2, width = "4cm") %>%
  column_spec(3, width = "3cm") %>%
  column_spec(6, width = "2cm") %>%
  column_spec(9, width = "2cm") %>%
  column_spec(10, width = "2cm") %>%
  column_spec(11, width = "3cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) 
```

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE,  escape = F)%>%
  column_spec(1, width = "2cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "3cm") %>%
  column_spec(6, width = "1.2cm") %>%
  column_spec(7, width = "1cm") %>%
  column_spec(8, width = ".7cm") %>%
  column_spec(9, width = ".7cm") %>%
  column_spec(10, width = "1.4cm") %>%
  column_spec(11, width = "1.4cm") %>%
  column_spec(12, width = "3cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
